Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-10 PAPER.tex
made josh edits until section 2.1

\author{
Carina Cheng\altaffilmark{1},
Aaron R. Parsons\altaffilmark{1,2},
Matthew Kolopanis \altaffilmark{3},
Daniel C. Jacobs\altaffilmark{3}, 
Saul A. Kohn\altaffilmark{4},
Adrian Liu\altaffilmark{1,5}, 
Jonathan C. Pober\altaffilmark{6}, 
James E.~Aguirre\altaffilmark{4},
Zaki S. Ali\altaffilmark{1}, 
Gianni Bernardi\altaffilmark{7,8,9}, 
Richard F. Bradley\altaffilmark{10,11,12},
Chris L. Carilli\altaffilmark{13,14},
David R. DeBoer\altaffilmark{2}, 
Matthew R. Dexter\altaffilmark{2},
Joshua S. Dillon\altaffilmark{1},
Pat Klima\altaffilmark{11},
David H. E. MacMahon\altaffilmark{2},
David F. Moore\altaffilmark{4},
Chuneeta D. Nunhokee\altaffilmark{8},
William P. Walbrugh\altaffilmark{7},
Andre Walker\altaffilmark{7}
}

@@

\begin{abstract}
The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and 
galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
develop techniques that help maximize sensitivity and validate results. Additionally, it is imperative to understand the trade-offs 
between different methods and their effects on common power spectrum themes. In this paper, we focus on three major 
themes --- signal loss, power spectrum error bar estimation, and bias in measurements. We describe techniques that affect 
these themes using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array 
for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result mostly stems from an 
updated signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
previously published PAPER analyses.
\end{abstract}

@@

By about one billion years after the Big Bang ($z \sim 6$), the very first stars and galaxies are thought to have ionized all the 
neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
into a plasma, is known as the epoch of reionization (EoR). The EoR is a relatively unexplored era in our cosmic dawn. Its 
history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
Direct measurements of the EoR would unlock powerful information about the intergalactic medium, revealing connections 
between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
web of galaxies we observe today \citep[for a review, see][]{furlanetto_et_al2006}.

One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}). This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations during this transformative era.

Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
the 21 cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and is forecasted to be able to make a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{deboer_et_al2017}).

The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three themes that are essential to investigate 
for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
from the lessons learned.

@@

Despite there being many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust 
methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.  In this 
paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
with each other and impact the themes. We will give brief definitions now, and build intuition for each theme in the sections to 
follow.

@@

A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
being standard steps in general $21$ cm analyses.
\begin{itemize}
\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}). This weighting has the effect of down-weighting correlated 
information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
weighting is in accurately defining a covariance matrix that best describes the data. We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
consider such as the independence of values in a dataset. We explore this potential pitfall of bootstrapping in Section \ref{sec:ErrorOverview}.
\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g. \citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}). An EoR detection must pass jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
\end{itemize}

@@

Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, and \citet{trott_et_al2016}. Before showing 
how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
analysis.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data 
distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
not exhibit loss.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

>>>>

\author{
Carina Cheng\altaffilmark{1}$^{,\diamond}$,
Aaron R. Parsons\altaffilmark{1,2},
Matthew Kolopanis \altaffilmark{3},
Daniel C. Jacobs\altaffilmark{3}, 
Saul A. Kohn\altaffilmark{4},
Adrian Liu\altaffilmark{1,5}$^{,\dagger}$, 
Jonathan C. Pober\altaffilmark{6}, 
James E.~Aguirre\altaffilmark{4},
Zaki S. Ali\altaffilmark{1}, 
Gianni Bernardi\altaffilmark{7,8,9}, 
Richard F. Bradley\altaffilmark{10,11,12},
Chris L. Carilli\altaffilmark{13,14},
David R. DeBoer\altaffilmark{2}, 
Matthew R. Dexter\altaffilmark{2},
Joshua S. Dillon\altaffilmark{1}$^{,*}$,
Pat Klima\altaffilmark{11},
David H. E. MacMahon\altaffilmark{2},
David F. Moore\altaffilmark{4},
Chuneeta D. Nunhokee\altaffilmark{8},
William P. Walbrugh\altaffilmark{7},
Andre Walker\altaffilmark{7}
}

@@

\begin{abstract}
The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
develop techniques that help maximize sensitivity while validating results. Additionally, it is imperative to understand the trade-offs 
between different methods and their effects on power spectrum estimates. In this paper, we focus on three major 
themes --- signal loss, power spectrum error estimation, and bias in measurements. We describe techniques that affect 
these themes using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array 
for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result mostly stems from an 
improved signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
previously published PAPER analyses.
\end{abstract}

@@

{\let\thefootnote\relax\footnote{$^{\diamond}$\href{mailto:ccheng@berkeley.edu}{ccheng@berkeley.edu}}}
{\let\thefootnote\relax\footnote{$^{\dagger}$Hubble Fellow}}
{\let\thefootnote\relax\footnote{$^{*}$NSF AAPF Fellow}}
\setcounter{footnote}{0}

By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
into a plasma, is known as the Epoch of Reionization (EoR). The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans from the birth of the first stars to the full reionization of the intergalactic medium (IGM). Its 
history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
web of galaxies we observe today \citep[for a review, see][]{furlanetto_et_al2006}.

One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}). This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21\,cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations.

Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and is forecast to be able to make a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics that are essential to investigate 
for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
from the lessons learned.

@@

Though there are many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust 
methods for determining accurate confidence intervals and rigorous techniques to identify and control systematics.  In this 
paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
with each other and impact the themes. We will give brief definitions now, and build intuition for each theme in the sections to 
follow.

@@

A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
being standard steps in general $21$ cm analyses.
\begin{itemize}
\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}). This weighting has the effect of down-weighting correlated 
information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
weighting is in accurately defining a covariance matrix that best describes the data. We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
itself (\citealt{andrae2010}). By randomly drawing many subsamples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
consider such as the independence of values in a dataset. We explore this potential pitfall of bootstrapping in Section \ref{sec:ErrorOverview}.
\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g. \citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}). An EoR detection must pass jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
\end{itemize}

@@

Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, and \citet{trott_et_al2016}. Before showing 
how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
analysis.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\hat{\textbf{p}}_{x}$. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
not exhibit loss.}
	\label{fig:sigloss_transfercurve}
\end{figure*}
